Indices Equations

### 2021-01-20 code/IndicesEquations.Rmd
Edited BhattacharyyaCoefficient function

```{r}
require(bio3d)
  BhattacharyyaDistance <- function(i1, i2){
    BhattacharyyaCoefficient <- bhattacharyya(cov(i1), cov(i2), q=99.9) #do we need a q value?
    distance <- -log(BhattacharyyaCoefficient)
    list(distance)
  }
```

>>>>

```{r}
require(bio3d)
  BhattacharyyaDCoefficient <- function(i1, i2){
    BC <- bhattacharyya(cov(i1), cov(i2)) #do we need a q value? 
    list(BC)
  } #does this function take the mean of the BC over the year? 
```
